---
title: "HW4"
author: "Sebastian Kirkpatrick"
date: "2024-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Question 1

```{r}
samp <- function(x, k) {
  n <- length(x)
  y <- c()
  
  for (i in 1:k) {
    j <- as.integer(runif(1,min=1,max=n-i+2))
    y[i] <- x[j]
    x[j] <- x[n + 1 - i]
  }
  
  return(y)
  
}
```

```{r}
x <- c(0,4,2,10)
samp(x,3)
```



# Question 2

a)

N ~ $Poisson(\lambda = 10)$

b)

$X_i$ ~ $Geometric(p = 0.8)$

c)

Y = $\sum_{i=1}^{N}X_i$

```{r}
n <- function(lam,n) {
  u <- runif(n)
  x <- qpois(u,lam)
  return(x)
}

xi <- function(p,n) {
  u <- runif(n)
  x <- qgeom(u,p)
  return(x)
}

yt <- function(p,lam,nsim) {
  Y <- c()
  N <- n(lam,nsim)
  
  for (i in 1:nsim) {
    XI <- xi(p, N[i])
    Y[i] <- sum(XI)
  }

  return(Y)
}


ez <- function(p, lam, nsim) {
  shoes <- c()
  c <- rpois(nsim, lam)
  for (i in 1:nsim) {
    shoe <- rgeom(c[i], p)
    shoes[i] <- sum(shoe)
  }
  return(shoes)
}

mean(yt(0.8, 10, 100000))
mean(ez(0.8, 10, 100000))
```
Just checking with the built in functions to make sure my runif() + cdf version works properly

d)

The probability of Y = 0 is the combined probability that no one comes in or that everyone who does come in buys the only pair they try on, which is $0.8^{n}$, where n is the number of customers that day. $E[0.8^{n}] =$ 

```{r}
exp(10 * (0.8 -1))
```

```{r}
set.seed(740)
mean(yt(0.8, 10, 1000000)==0)
mean(ez(0.8, 10, 1000000)==0)
```
P(Y=0) $\approx$ .135



# Question 3

a)

```{r}
g <- function(x) {
  -(x^4) + 16
}

q3 <- function(n) {
  x <- runif(n,-2,2)
  y <- g(x)
  c <- 4 * (1/n) * sum(y)
  return(c)
}

set.seed(740)
q3(100000)
```
C $\approx$ 51.18

b)

```{r}
pdf <- function(x) {
  out <- (16 - x^4) / 51.18
  return(out)
}

cdf <- function(x) {
  ((16 * x) / 51.18) - ((x^5) / (51.18 * 5)) + 0.5
}


icdf <- function(p) {
  f <- function(x, p) {
    abs(cdf(x) - p)
  }
  
  optimize(f, lower=-2, upper=2, p=p)$minimum
}

icdf <- Vectorize(icdf)


set.seed(740)
u <- runif(100)
icdf(u)
min(icdf(u))
max(icdf(u))
```

c)

```{r}
pdf(0)

region <- function(n) {
  val <- c()
  x <- runif(n, -2, 2)
  y <- runif(n, 0, pdf(0))
  
  for (i in 1:n) {
    if (y[i] < pdf(x[i])) {
      val <- c(val, x[i])
    }
  }
  
  return(val)
  }

accepted <- region(10000)
hist(accepted)
```



# Question 4

a)

```{r}
stupid_grad_question <- function(n, alpha) {
  u <- runif(n)
  x <- alpha * tan((u - 0.5) * pi)
  return(x)
}

stupid_grad_question(10, 1)
```

b)

```{r}
a <- dnorm(0)
b <- dcauchy(0)

a/b

region4 <- function(n, alpha) {
  val <- c()
  x <- runif(n,-5,5)
  y <- runif(n,0, 1.5 * dcauchy(0))
  
  c_pdf <- function(x,alpha){
    return(alpha / ((alpha^2 + x^2) * pi))
  }
  
  for (i in 1:n) {
    if (y[i] < dnorm(x[i])) {
      val <- c(val, x[i])
    }
  }
  
  return(val)
  }

accepted4 <- region4(10000, 1)
hist(accepted4)
```

Not a fan of this hw. We can talk on the plane for better ideas